Registered Report

### 2024-11-07 Registered Report.Rmd
Starting registered report
Minor updates for paper summary. For registered report, added scatterplots with q score matching that represent different "types" of assortative mating.

```{r Data Simulation}
q_maternal <- rbeta(1000, 0.5, 0.5)
q_paternal <- rbeta(1000, 0.5, 0.5)
plot(density(q_maternal))

>>>>

```{r test}
# Set a seed for reproducibility
set.seed(123)

# Create two datasets, `q_maternal` and `q_paternal`, each with 1000 data points following a beta distribution
q_maternal <- rbeta(1000, 1, 1)
q_paternal <- rbeta(1000, 1, 1)

# Create a new dataset, `sampled_q_maternal`, by sampling 500 q scores without replacement from the `q_maternal` dataset
sampled_q_maternal <- sample(q_maternal, 500, replace=FALSE)

# Create a new variable, `sampled_q_paternal`, by sampling 500 q scores from the `q_paternal` dataset
# Use the `ifelse()` function to set the probability of selecting a q score from `q_paternal` based on the corresponding q score in `sampled_q_maternal`
sampled_q_paternal <- sapply(sampled_q_maternal, function(x) {
  if (x >= 0.5) {
    sample(q_paternal[q_paternal >= 0.5], 1, prob = rep(0.9 / length(q_paternal[q_paternal >= 0.5]), length(q_paternal[q_paternal >= 0.5])))
  } else {
    sample(q_paternal[q_paternal < 0.5], 1, prob = rep(0.1 / length(q_paternal[q_paternal < 0.5]), length(q_paternal[q_paternal < 0.5])))
  }
})

# Create a new dataframe, `q_scores_df`, by combining `sampled_q_maternal` and `sampled_q_paternal`
q_scores_df <- data.frame(sampled_q_maternal, sampled_q_paternal)

# Plot a scatterplot of `sampled_q_paternal` versus `sampled_q_maternal` to visualize the relationship between the two variables
plot(sampled_q_maternal, sampled_q_paternal, xlab="Sampled Maternal q scores", ylab="Sampled Paternal q scores", main="Scatterplot of Maternal vs Paternal q scores")
```

```{r test 2}
# Set a seed for reproducibility
set.seed(123)

# Create two datasets, `q_maternal` and `q_paternal`, each with 1000 data points following a beta distribution
q_maternal <- rbeta(1000, 1, 1)
q_paternal <- rbeta(1000, 1, 1)

# Create a new dataset, `sampled_q_maternal`, by sampling 500 q scores without replacement from the `q_maternal` dataset
sampled_q_maternal <- sample(q_maternal, 500, replace=FALSE)

# Create a new variable, `sampled_q_paternal`, by sampling 500 q scores from the `q_paternal` dataset
# Use the `ifelse()` function to set the probability of selecting a q score from `q_paternal` based on the corresponding q score in `sampled_q_maternal`
sampled_q_paternal <- sapply(sampled_q_maternal, function(x) {
  if (x <= 0.5) {
    # If the maternal q score is less than or equal to 0.5, sample from the lower half of the paternal q scores with higher probability
    sample(q_paternal[q_paternal <= 0.5], 1, prob = ifelse(q_paternal[q_paternal <= 0.5] <= 0.25, 0.9, 0.1))
  } else {
    # If the maternal q score is greater than 0.5, sample from the upper half of the paternal q scores with higher probability
    sample(q_paternal[q_paternal > 0.5], 1, prob = ifelse(q_paternal[q_paternal > 0.5] >= 0.75, 0.9, 0.1))
  }
})

# Create a new dataframe, `q_scores_df`, by combining `sampled_q_maternal` and `sampled_q_paternal`
q_scores_df <- data.frame(sampled_q_maternal, sampled_q_paternal)

# Plot a scatterplot of `sampled_q_paternal` versus `sampled_q_maternal` to visualize the relationship between the two variables
plot(sampled_q_maternal, sampled_q_paternal, xlab="Sampled Maternal q scores", ylab="Sampled Paternal q scores", main="Scatterplot of Maternal vs Paternal q scores")
```
```{r Data Simulation}
# Simulate q score data for maternal and paternal species in a beta distribution with a random mating pattern to draw samples from. 
q_maternal <- rbeta(1000, 1, 1)
q_paternal <- rbeta(1000, 1, 1)

# Visualize random mating pattern following a beta distribution
hist(q_paternal)
hist(q_maternal)

# Sample and group q scores to indicate predicted mating patterns 
maternal_random <- sample(q_maternal, 500, replace = FALSE)
